Papers

### 2025-10-24 papers.qmd
add JASA paper
add TIES talk

J. E. Borgert, J. Hannig, **J. D. Tucker**, L. Arbeeva, A. N. Buck, Y. M. Golightly, S. P. Messier, A. E. Nelson, and J. S. Marron, "Elastic Shape Analysis of Movement Data", *JASA Case Studies and Applications*, accepted, 2025. [arxiv preprint](https://arxiv.org/abs/2409.13938)

@@

## Invited Talks
"Bayesian Model Calibration: An Elastic Approach" *Colorado State University Statistics Seminar*, April 28, 2025, [Slides](https://jdtuck.github.io/presentations/CSU_April25/CSU_April25.html)

@@

"Elasic Bayesian Model Calibration" *ASA SDNS Webinar*, December 04, 2023, [Slides](https://jdtuck.github.io/presentations/ASA_23_Calibration/index.html)

>>>>

J. E. Borgert, J. Hannig, **J. D. Tucker**, L. Arbeeva, A. N. Buck, Y. M. Golightly, S. P. Messier, A. E. Nelson, and J. S. Marron, "Elastic Shape Analysis of Movement Data", *JASA Case Studies and Applications*, 10.1080/01621459.2025.2572778, 2025. [PDF](Papers/JASA25_Borgert.pdf)

@@

## Invited Talks
"Elastic Functional Changepoint Detection of Climate Impacts from Localized Sources" *Environmentrics TIES Webinar*, October 24, 2025, [Slides](https://jdtuck.github.io/presentations/TIES_Webinar_Oct_25/TIES_Webinar_Oct25.html) [Video](https://www.youtube.com/@environmetricswebinar3128)

"Bayesian Model Calibration: An Elastic Approach" *Colorado State University Statistics Seminar*, April 28, 2025, [Slides](https://jdtuck.github.io/presentations/CSU_April25/CSU_April25.html)

@@

"Elasic Bayesian Model Calibration" *ASA SDNS Webinar*, December 04, 2023, [Slides](https://jdtuck.github.io/presentations/ASA_23_Calibration/index.html) [Video](https://www.youtube.com/watch?v=UNyOfL_zLX8&t=1469s)
